---
title: "<span class='title'>R II: Programming</span>"
subtitle: "<span class='subtitle'>Data Wrangling</span>"
author: "<span class='author'>Michael Clark</span>"
institute: "<span class='institute'>m-clark.github.io <br> @statsdatasci <br> CSCAR, UM</span>"
date: "<span class='date'>2020-10-13</span>"
css: style.css
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: zenburn
      highlightLines: true
      countIncrementalSlides: false
---
class: inverse

background-image: url(https://github.com/m-clark/m-clark.github.io/raw/master/img/Rlogo.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, crayon.enabled = FALSE) # see https://github.com/hadley/mastering-shiny/issues/132

knitr::opts_chunk$set(
  # code
  echo      = T,
  eval      = F,
  message   = F,
  warning   = F,
  error     = F,
  comment   = NA,
  R.options = list(width = 220),
  # viz
  dev.args  = list(bg = 'transparent'),
  dev       = 'svglite',
  fig.align = 'center',
  out.width = '75%',
  fig.asp   = .75,
  # cache
  cache.rebuild = F,
  cache         = F
)

kable_df = function(data, digits=3, ...) {
  kableExtra::kable(
    data,
    digits = digits,
    format = 'html',
    booktabs = T,
    # longtable = F,
    linesep = "",
    ...,
  ) %>% 
    kableExtra::kable_styling(full_width = F)
}

perc = function(x, digits = 1) paste(rnd(x*100, digits = digits), '%')
```

```{r setup-logo, echo=FALSE, eval=TRUE}
# DOESN'T DISPLAY WITH INVERSE
# xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
#https://raw.githubusercontent.com/m-clark/m-clark.github.io/master/img/mc_logo.png
xaringanExtra::use_logo(
  image_url = 'https://raw.githubusercontent.com/m-clark/m-clark.github.io/master/img/mc_logo.png', 
  link_url = 'https://m-clark.github.io',
  width = '5%', 
  position =  xaringanExtra::css_position(bottom = "-2em", left = "1em"),
  exclude_class = c("title-slide")
)
```



```{r setup-packs}
library(tidyverse)
```


---
class: inverse, middle, center





### *Basics*

### *Iterative Programming*

### *Writing Functions*

### *More*


---
class: inverse middle center

# Basics
<br>
<br>
<i class="fas fa-laptop-code fa-5x"></i>

---
class: inverse 

# Basics: Objects

```{r}
library(tidyverse)
str(diamonds)
glimpse(diamonds)
```

---
class: inverse 

# Basics: Documentation

```{r help}
sample(?)
```


---
class: inverse 

# Basics:


---
class: inverse 

# Basics:



---
class: inverse middle  center

# Iterative Programming
<br>
<br>
<i class="fas fa-sync-alt fa-5x"></i>

---
class: inverse  center
---
class: inverse middle  center

# Functions

<br>
<br>

<i class="fa fa-code fa-5x"></i>


---
class: inverse middle  center

# Iterative Programming
<br>
<br>
<i class="fab fa-r-project fa-5x"></i>


---
class: last-slide, inverse, center, middle



![](https://github.com/m-clark/m-clark.github.io/raw/master/img/Rlogo.svg)


